Data_Analysis_MS_ddm_exp1

### 2018-07-10 Replication/Results/data_analysis/preproc/MS_rep_prepro.rmd
revisit the results

setwd(ddmDir)
write.csv(df.M.hddm_m,'exp7_rep_match_hddm.csv',row.names = F)
write.csv(df.M.hddm_nm,'exp7_rep_mismatch_hddm.csv',row.names = F)
write.csv(df.C.hddm_val,'exp7_rep_categ_val_hddm.csv',row.names = F)
write.csv(df.C.hddm_id,'exp7_rep_categ_id_hddm.csv',row.names = F)
rm('df.M.hddm','df.C.hddm','df.M.hddm_m','df.M.hddm_nm','df.C.hddm_val','df.C.hddm_id')
setwd(curDir)

@@

# write files
setwd(traDir)
write.csv(df.M1.V.sum_w,'exp7_rep_match_behav_wide.csv',row.names = F)
write.csv(df.M1.V.SDT_l,'exp7_rep_match__dprime_long.csv',row.names = F)
write.csv(df.M1.V.sum_rt_acc_l,'exp7_rep_match__rt_acc_long.csv',row.names = F)
setwd(curDir)

@@

# write files to an upper-lelel folder
setwd(traDir)
write.csv(df.C1.V.sum_w,'exp7_rep_categ_behav_wide.csv',row.names = F)
write.csv(df.C1.V.sum_noTask_w,'exp7_rep_categ_behav_noTask_wide.csv',row.names = F)
write.csv(df.C1.V.sum_rt_acc_l,'exp7_rep_categ__rt_acc_long.csv',row.names = F)
write.csv(df.v.sum_eff_all_w,'exp7_cross_taskeffect_wide.csv',row.names = F)
setwd(curDir)
```

```{r plot_match_RT_data,echo=FALSE,warning=FALSE, message=FALSE}
MSplots(saveDir = traDir, curDir = curDir, task = 'match',type = 'RT', inData = df.M1.V.sum_rt_acc_l)
#RTdata1 <- df.M1.V.sum_rt_acc_l %>%
#  select(Subject,Match,Morality,Identity,RT) %>% 
#  filter(Match == "match" & Morality == "Good")
#RTdata1$Identity <- factor(RTdata1$Identity,levels = c("Self","Other"))
#p1 <- ggplot(data = RTdata1, aes(y = RT, x = Identity,fill = Identity)) +
#  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
#  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
#  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
#  guides(fill = FALSE) +guides(color = FALSE)+
#  theme_bw() +
#  raincloud_theme+scale_y_continuous(limits = c(300,900))+labs(x = "Good",y = "Reaction times(ms)")
#RTdata2 <- df.M1.V.sum_rt_acc_l %>%
#  select(Subject,Match,Morality,Identity,RT) %>% 
#  filter(Match == "match" & Morality == "Bad")
#RTdata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
#p2 <- ggplot(data = RTdata2, aes(y = RT, x = Identity,fill = Identity)) +
#  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
#  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
#  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
#  guides(fill = FALSE) +guides(color = FALSE)+
#  theme_bw() +
#  raincloud_theme+scale_y_continuous(limits = c(300,900),breaks = NULL)+labs(x = "Bad",y = "")

#setwd(traDir)
#tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
#p_rt_match <- multiplot(p1,p2,cols = 2)
#dev.off()
#setwd(curDir)
#multiplot(p1,p2,cols = 2)
```

>>>>

setwd(ddmDir)
write.csv(df.M.hddm_m,'MS_rep_match_hddm.csv',row.names = F)
write.csv(df.M.hddm_nm,'MS_rep_mismatch_hddm.csv',row.names = F)
write.csv(df.C.hddm_val,'MS_rep_categ_val_hddm.csv',row.names = F)
write.csv(df.C.hddm_id,'MS_rep_categ_id_hddm.csv',row.names = F)
rm('df.M.hddm','df.C.hddm','df.M.hddm_m','df.M.hddm_nm','df.C.hddm_val','df.C.hddm_id')
setwd(curDir)

@@

# write files
setwd(traDir)
write.csv(df.M1.V.sum_w,'MS_rep_match_behav_wide.csv',row.names = F)
write.csv(df.M1.V.SDT_l,'MS_rep_match__dprime_long.csv',row.names = F)
write.csv(df.M1.V.sum_rt_acc_l,'MS_rep_match__rt_acc_long.csv',row.names = F)
setwd(curDir)

@@

# write files to an upper-lelel folder
setwd(traDir)
write.csv(df.C1.V.sum_w,'MS_rep_categ_behav_wide.csv',row.names = F)
write.csv(df.C1.V.sum_noTask_w,'MS_rep_categ_behav_noTask_wide.csv',row.names = F)
write.csv(df.C1.V.sum_rt_acc_l,'MS_rep_categ__rt_acc_long.csv',row.names = F)
write.csv(df.v.sum_eff_all_w,'MS_cross_taskeffect_wide.csv',row.names = F)
setwd(curDir)
```

```{r plot_match_RT_data,echo=FALSE,warning=FALSE, message=FALSE}
MSplots(saveDir = traDir, curDir = curDir, task = 'match',type = 'RT', inData = df.M1.V.sum_rt_acc_l)

### 2018-07-10 Results/preproc/MS_ddm_preproc.rmd
revisit the results

# wide-format
df.C1.V.acc_w  <- dcast(df.C1.V.acc, Subject ~ Task + Morality + Identity ,value.var = "ACC")

# rename the column number
colnames(df.C1.V.acc_w)[2:9] <- paste("ACC", colnames(df.C1.V.acc_w[,2:9]), sep = "_")

@@

# combine data cross task
# tmp <- aggregate(df.C1.V.acc[,7],list(df.C1.V.acc$Subject,df.C1.V.acc$Morality,df.C1.V.acc$Identity),mean)
df.C1.V.acc.noTask <- summarySE(df.C1.V.acc,measurevar = 'ACC',groupvars = c('Subject','Morality','Identity'))
df.C1.V.acc.noTask_w <- dcast(df.C1.V.acc.noTask, Subject ~  Morality + Identity  ,value.var = "ACC")

df.C1.V.acc.noTask_w$good_bad_slf <- df.C1.V.acc.noTask_w$Good_Self - df.C1.V.acc.noTask_w$Bad_Self
df.C1.V.acc.noTask_w$good_bad_oth <- df.C1.V.acc.noTask_w$Good_Self - df.C1.V.acc.noTask_w$Bad_Other
df.C1.V.acc.noTask_w$slf_oth_good <- df.C1.V.acc.noTask_w$Good_Self - df.C1.V.acc.noTask_w$Good_Other
df.C1.V.acc.noTask_w$slf_oth_bad <- df.C1.V.acc.noTask_w$Bad_Self - df.C1.V.acc.noTask_w$Bad_Other

@@

# write files to an upper-lelel folder
setwd(traDir)
write.csv(df.C1.V.sum_w,'MS_categ_behav_wide.csv',row.names = F)
write.csv(df.C1.V.sum_noTask_w,'MS_categ_behav_noTask_wide.csv',row.names = F)
write.csv(df.C1.V.sum_rt_acc_l,'MS_categ__rt_acc_long.csv',row.names = F)
write.csv(df.v.sum_eff_all_w,'MS_cross_taskeffect_wide.csv',row.names = F)
setwd(curDir)
```

@@

>>>>

# wide-format
df.C1.V.acc_w  <- dcast(df.C1.V.acc, Subject ~ Task + Morality + Identity ,value.var = "ACC")
# rename the column number
colnames(df.C1.V.acc_w)[2:9] <- paste("ACC", colnames(df.C1.V.acc_w[,2:9]), sep = "_")

@@

# combine data cross task
# tmp <- aggregate(df.C1.V.acc[,7],list(df.C1.V.acc$Subject,df.C1.V.acc$Morality,df.C1.V.acc$Identity),mean)
#df.C1.V.acc.noTask <- summarySE(df.C1.V.acc,measurevar = 'ACC',groupvars = c('Subject','Morality','Identity'))
#df.C1.V.acc.noTask_w <- dcast(df.C1.V.acc.noTask, Subject ~  Morality + Identity  ,value.var = "ACC")

df.C1.V.acc_noTask_w$good_bad_slf <- df.C1.V.acc_noTask_w$ACC_Good_Self - df.C1.V.acc_noTask_w$ACC_Bad_Self
df.C1.V.acc_noTask_w$good_bad_oth <- df.C1.V.acc_noTask_w$ACC_Good_Self - df.C1.V.acc_noTask_w$ACC_Bad_Other
df.C1.V.acc_noTask_w$slf_oth_good <- df.C1.V.acc_noTask_w$ACC_Good_Self - df.C1.V.acc_noTask_w$ACC_Good_Other
df.C1.V.acc_noTask_w$slf_oth_bad <- df.C1.V.acc_noTask_w$ACC_Bad_Self - df.C1.V.acc_noTask_w$ACC_Bad_Other

@@

# merge the RT and ACC data without task (long-format) ####
df.C1.V.sum_rt_acc_noTask_l <- merge(df.C1.V.acc_noTask,df.C1.V.RT.subj_noTask,by = c("Subject","Morality",'Identity'))
df.C1.V.sum_rt_acc_noTask_l <- df.C1.V.sum_rt_acc_noTask_l[order(df.C1.V.sum_rt_acc_noTask_l$Subject),]

df.C1.V.sum_rt_acc_noTask_l <- df.C1.V.sum_rt_acc_noTask_l[,c("Subject","Morality",'Identity',"N.x","countN","ACC","RT")]
colnames(df.C1.V.sum_rt_acc_noTask_l) <- c("Subject","Morality",'Identity',"Ntrials","corrTrials","ACC","RT")

# write files to an upper-lelel folder
setwd(traDir)
write.csv(df.C1.V.sum_w,'MS_categ_behav_wide.csv',row.names = F)
write.csv(df.C1.V.sum_noTask_w,'MS_categ_behav_noTask_wide.csv',row.names = F)
write.csv(df.C1.V.sum_rt_acc_l,'MS_categ__rt_acc_long.csv',row.names = F)
write.csv(df.C1.V.sum_rt_acc_noTask_l,'MS_categ__rt_acc_noTask_long.csv',row.names = F)
write.csv(df.v.sum_eff_all_w,'MS_cross_taskeffect_wide.csv',row.names = F)
setwd(curDir)
```

@@

```{r plot_noTask_data,echo=FALSE,warning=FALSE, message=FALSE}
# plot ACC
MSplots(saveDir = traDir, curDir = curDir, task = 'categ',type = 'ACC', inData = df.C1.V.sum_rt_acc_noTask_l)
# plot RT
MSplots(saveDir = traDir, curDir = curDir, task = 'categ',type = 'RT', inData = df.C1.V.sum_rt_acc_noTask_l)
```
